State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-22 prism-backend/research/soa_review/ac.tex
Added review of CKLM14.

@@

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
  different approach?
\end{itemize}

>>>>

\item[\cite{cklm14}:] This work is, in essence, a generalization of \cite{bcc+09}.
  The main novel building block are controlled-malleability NIZKs. Basically,
  these are NIZKs that can be re-randomized, but only for a pre-defined set of
  (NP) transformations. From this cm-NIZKs, malleable signatures are built.
  From malleable signatures and commitments, delegatable credentials are built
  as follows. Credentials are basically a tuple $(nym, l, flag)$, where $nym$
  is a commitment to the user's private key, $l$ is the length of the credential
  in the delegation chain, and $flag$ is either $cred$ or $proof$. Credentials
  are accompanied with a malleable signature (which, for level 1 credentials,
  it is a signature by the issuer). To create ``proofs'' or to delegate, the
  credential owner has to apply one of the two allowed transformations. For
  ``proofs'', basically the transformation that has to be applied to the original
  proof (malleable signature) converts it to a proof showing that the prover
  knows the secret in the ``source'' pseudonym and ``target'' pseudonym, and
  both are the same. In the case of delegations, flag is set to ``cred'', and
  the transformation converts the cm-NIZK proof into one that lets the prover
  prove knowledge of the secret key in the ``source'' pseudonym, and allows
  only to produce a new credential with structure $(nym', l+1, cred)$ -- i.e.,
  from a credential of level $l$, only a credential of level $l+1$ can be
  derived. On the delegation topic, the type of delegation this work ``supports'',
  at least by default, is the simple one of hierarchical delegation.

@@

\item[\cite{cklm14}:] Defines security of the DAC scheme using simulation-based
  notions of anonymity and unforgeability.

@@

\begin{itemize}
\item : Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
  different approach?
\end{itemize}
